Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-05-20 document/ms.tex
listing assumptions in discussion

\dfmtodo{write this section, eh?}

>>>>

In our analysis we make a few simplifying assumptions.
Each of these could be relaxed and \dfmtodo{BLAH BLAH BLAH}.
\begin{itemize}

\item {\bf Conditional independence}\quad
We assumed that every object in the catalog was a conditionally independent
Poisson draw from the observable occurrence rate function.
This is an interesting assumption to consider when applying this method to a
different catalog where multiple transiting systems are included.
In practice, the best first step towards relaxing this assumption is probably
to follow \citet{tremaine} and assume that the mutual inclination distribution
is the only source of conditional dependence between planets.
For this \paper, the assumption of conditional independence is justified
because the dataset explicitly includes only systems with a single transiting
exoplanet.

\item {\bf False positives}\quad

\item {\bf Known observational uncertainties}\quad

\item {\bf Given empirical detection efficiency}\quad

\item {\bf Smooth rate function}\quad

\end{itemize}
